### 2021-11-15 src/ms.tex
initial commit

% Define document class
\documentclass[twocolumn]{aastex631}

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

% Title
\title{\texttt{showyourwork}: a workflow for open source scientific articles}

% Author list
\author[0000-0000-0000-0000]{Rodrigo Luger}

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

% Main body with filler text
\section{Introduction}
\Blindtext[4]

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/HD118203_transit.pdf}
        \caption{
            Caption.
        }
        \label{fig:HD118203_transit}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/HD118203_corner.pdf}
        \caption{
            Caption.
        }
        \label{fig:HD118203_corner}
    \end{centering}
\end{figure}

\end{document}

### 2021-11-15 src/analysis/HD118203.py

@@ -1,0 +1,121 @@
+import exoplanet as xo
+import numpy as np
+import lightkurve as lk
+import matplotlib.pyplot as plt
+import pymc3 as pm
+import aesara_theano_fallback.tensor as tt
+import pymc3_ext as pmx
+from celerite2.theano import terms, GaussianProcess
+import warnings
+import logging
+
+
+# Suppress exoplanet & theano warnings
+logging.getLogger("theano.tensor.opt").setLevel(logging.ERROR)
+warnings.filterwarnings(action="ignore", category=UserWarning, module="exoplanet")
+
+
+# Download the light curve
+lcfs = lk.search_lightcurve(
+    "TIC 286923464", mission="TESS", author="SPOC"
+).download_all(flux_column="pdcsap_flux")
+lc = lcfs.stitch().remove_nans().remove_outliers(sigma=7)
+x = np.ascontiguousarray(lc.time.value, dtype=np.float64)
+y = np.ascontiguousarray(1e3 * (lc.flux - 1), dtype=np.float64)
+yerr = np.ascontiguousarray(1e3 * lc.flux_err, dtype=np.float64)
+texp = np.min(np.diff(x))
+
+# Run Box Least Squares (BLS) to obtain a guess for the planet period
+pg = xo.estimators.bls_estimator(x, y, yerr, min_period=2, max_period=20)
+peak = pg["peak_info"]
+period_guess = peak["period"]
+t0_guess = peak["transit_time"]
+depth_guess = peak["depth"]
+
+# Mask out-of-transit data
+transit_mask = (
+    np.abs((x - t0_guess + 0.5 * period_guess) % period_guess - 0.5 * period_guess)
+    < 0.25
+)
+x = np.ascontiguousarray(x[transit_mask])
+y = np.ascontiguousarray(y[transit_mask])
+yerr = np.ascontiguousarray(yerr[transit_mask])
+
+# Define our pymc3 model
+with pm.Model() as model:
+
+    # Stellar parameters
+    mean = pm.Normal("mean", mu=0.0, sigma=10.0)
+    u = xo.QuadLimbDark("u")
+    star_params = [mean, u]
+
+    # Gaussian process noise model
+    sigma = pm.InverseGamma("sigma", alpha=3.0, beta=2 * np.median(yerr))
+    log_sigma_gp = pm.Normal("log_sigma_gp", mu=0.0, sigma=10.0)
[…]

### 2021-11-15 src/figures/HD118203_corner.py

@@ -1,0 +1,13 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import corner
+
+# Load the results
+data = np.load("../data/HD118203.npz")
+samples = data["samples"]
+
+# Plot the corner
+fig = corner.corner(
+    samples, labels=["period", "ror", "b"], truths=[6.134980, 0.05538, 0.125]
+)
+fig.savefig("HD118203_corner.pdf", bbox_inches="tight")

### 2021-11-15 src/figures/HD118203_transit.py

@@ -1,0 +1,23 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Load the results
+data = np.load("../data/HD118203.npz")
+x = data["x"]
+y = data["y"]
+gp_pred = data["gp_pred"]
+lc_pred = data["lc_pred"]
+map_t0 = data["map_t0"]
+map_period = data["map_period"]
+map_mean = data["map_mean"]
+
+# Plot the transit
+fig = plt.figure(figsize=(8, 4))
+x_fold = (x - map_t0 + 0.5 * map_period) % map_period - 0.5 * map_period
+inds = np.argsort(x_fold)
+plt.scatter(x_fold, y - gp_pred - map_mean, c="k", s=3, alpha=0.5)
+plt.plot(x_fold[inds], lc_pred[inds] - map_mean, "C0")
+plt.xlabel("time since transit [days]")
+plt.ylabel("relative flux [ppt]")
+_ = plt.xlim(-0.25, 0.25)
+fig.savefig("HD118203_transit.pdf", bbox_inches="tight")

### 2021-12-17 src/ms.tex
test error log upload
fix error
update

@@
 % Author list
-\author[0000-0000-0000-0000]{Rodrigo Luger}
+\author[0000-0002-0296-3826]{Rodrigo Luger}
 
@@
         \includegraphics[width=0.75\linewidth]{figures/HD118203_transit.pdf}
+        \includegraphics[width=0.75\linewidth]{figures/HD118203_corner.pdf}
         \caption{
-            Caption.
+            Automatically-generated figures showing the transit of HD 118203b in \emph{TESS} (\emph{top}) and the joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}).
+Both figures were generated from the same \texttt{Python} script in the \texttt{src/figures} directory (linked to in the \texttt{GitHub} icon in the margin).
+The other margin icon indicates that these figures depend on a dataset (a \texttt{.npz} file containing the posterior samples),
+            which is automatically generated by \showyourwork and uploaded to Zenodo.
+Users wishing to reproduce the results in this paper can choose whether to re-generate this dataset or download a static version from Zenodo (linked to in the margin).
         }
-        \label{fig:HD118203_transit}
+        \label{fig:HD118203}
     \end{centering}
@@
     \begin{centering}
-        \includegraphics[width=0.75\linewidth]{figures/HD118203_corner.pdf}
+        \includegraphics[width=0.75\linewidth]{static/eclipse.jpeg}
         \caption{
-            Caption.
+            A static figure committed to the repository showing a total solar eclipse. 
+            Since this figure is in the \texttt{src/static} directory, \showyourwork knows not to attempt to generate it. 
+            By default, margin icons are not added to static figures.
+            Here we manually add icons linking to the original photograph and its license using the \texttt{\textbackslash marginicon} command.
         }
-        \label{fig:HD118203_corner}
+        \marginicon{%
+            \stackon[3pt]{%
+                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg}{\color{sywBlue}\faWikipediaW}%
+            }{%
+                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg\#Licensing}{\color{sywBlue}\faCreativeCommons}%
+            }%
+        }
+        \label{fig:eclipse}
     \end{centering}

### 2021-12-17 src/analysis/HD118203.py

@@ -1,7 +1,6 @@
 import exoplanet as xo
 import numpy as np
 import lightkurve as lk
-import matplotlib.pyplot as plt
 import pymc3 as pm
 import aesara_theano_fallback.tensor as tt
 import pymc3_ext as pmx
@@ -9,11 +8,9 @@ from celerite2.theano import terms, GaussianProcess
 import warnings
 import logging
 
-
 # Suppress exoplanet & theano warnings
 logging.getLogger("theano.tensor.opt").setLevel(logging.ERROR)
 warnings.filterwarnings(action="ignore", category=UserWarning, module="exoplanet")
-
 
 # Download the light curve
 lcfs = lk.search_lightcurve(

### 2021-12-17 src/figures/HD118203.py

@@ -1,0 +1,54 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import corner
+
+# Load the results
+data = np.load("../data/HD118203.npz")
+x = data["x"]
+y = data["y"]
+gp_pred = data["gp_pred"]
+lc_pred = data["lc_pred"]
+map_t0 = data["map_t0"]
+map_period = data["map_period"]
+map_mean = data["map_mean"]
+samples = data["samples"]
+
+# Plot the transit
+fig = plt.figure(figsize=(8, 4))
+x_fold = (x - map_t0 + 0.5 * map_period) % map_period - 0.5 * map_period
+inds = np.argsort(x_fold)
+plt.scatter(x_fold, y - gp_pred - map_mean, c="k", s=3, alpha=0.5)
+plt.plot(x_fold[inds], lc_pred[inds] - map_mean, "C0")
+plt.xlabel("time since transit [days]", fontsize=12)
+plt.ylabel("relative flux [ppt]", fontsize=12)
+_ = plt.xlim(-0.25, 0.25)
+fig.savefig("HD118203_transit.pdf", bbox_inches="tight")
+
+# Plot the corner plot (with some appearance tweaks)
+samples[:, 0] -= 6.13498
+samples[:, 0] *= 1e5
+fig = corner.corner(
+    samples,
+    labels=[
+        "$\mathrm{period} - 6.13498$ [days]",
+        "planet/star radius ratio",
+        "impact parameter",
+    ],
+    truths=[0, 0.05538, 0.125],
+)
+fig.axes[6].set_xticks([-4, -2, 0, 2, 4])
+fig.axes[6].set_xticklabels(
+    [
+        r"$-4 \times 10^{-5}$",
+        r"$-2 \times 10^{-5}$",
+        0,
+        r"$2 \times 10^{-5}$",
+        r"$4 \times 10^{-5}$",
+    ]
+)
+for axis in fig.axes:
+    for tick in axis.xaxis.get_major_ticks() + axis.yaxis.get_major_ticks():
+        tick.label.set_fontsize(6)
+    axis.set_xlabel(axis.get_xlabel(), fontsize=12)
+    axis.set_ylabel(axis.get_ylabel(), fontsize=12)
+fig.savefig("HD118203_corner.pdf", bbox_inches="tight")

### 2021-12-17 src/figures/HD118203_corner.py

@@ -1,13 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import corner
-
-# Load the results
-data = np.load("../data/HD118203.npz")
-samples = data["samples"]
-
-# Plot the corner
-fig = corner.corner(
-    samples, labels=["period", "ror", "b"], truths=[6.134980, 0.05538, 0.125]
-)
-fig.savefig("HD118203_corner.pdf", bbox_inches="tight")

### 2021-12-17 src/figures/HD118203_transit.py

@@ -1,23 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-# Load the results
-data = np.load("../data/HD118203.npz")
-x = data["x"]
-y = data["y"]
-gp_pred = data["gp_pred"]
-lc_pred = data["lc_pred"]
-map_t0 = data["map_t0"]
-map_period = data["map_period"]
-map_mean = data["map_mean"]
-
-# Plot the transit
-fig = plt.figure(figsize=(8, 4))
-x_fold = (x - map_t0 + 0.5 * map_period) % map_period - 0.5 * map_period
-inds = np.argsort(x_fold)
-plt.scatter(x_fold, y - gp_pred - map_mean, c="k", s=3, alpha=0.5)
-plt.plot(x_fold[inds], lc_pred[inds] - map_mean, "C0")
-plt.xlabel("time since transit [days]")
-plt.ylabel("relative flux [ppt]")
-_ = plt.xlim(-0.25, 0.25)
-fig.savefig("HD118203_transit.pdf", bbox_inches="tight")

### 2021-12-17 src/ms.tex
tweaks

@@
 % Title
-\title{\texttt{showyourwork}: a workflow for open source scientific articles}
+\title{\showyourwork: a workflow for open source scientific articles}
 
@@
             By default, margin icons are not added to static figures.
-            Here we manually add icons linking to the original photograph and its license using the \texttt{\textbackslash marginicon} command.
+            Here we manually add icons linking to the original photograph on Wikimedia Commons and its license using the \texttt{\textbackslash marginicon} command.
         }

### 2021-12-17 src/ms.tex
showcasing other papers

@@
 \section{Introduction}
-\Blindtext[4]
 
@@
     \begin{centering}
-        \includegraphics[width=0.75\linewidth]{figures/HD118203_transit.pdf}
-        \includegraphics[width=0.75\linewidth]{figures/HD118203_corner.pdf}
+        \includegraphics[width=\linewidth]{figures/role_eccentricity.pdf}
         \caption{
-            Automatically-generated figures showing the transit of HD 118203b in \emph{TESS} (\emph{top}) and the joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}).
+            LEGWORK plot. Figure reproduced from \citet{Wagg2021}.
+        }
+        \label{fig:role_eccentricity}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+        \caption{
+            Caption. Figure adapted from \citet{Luger2021}; data originally from \citet{Crossfield2014}.
+        }
+        \label{fig:luhman16b}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/HD118203_transit.pdf}
+        \includegraphics[width=\linewidth]{figures/HD118203_corner.pdf}
+        \caption{
+            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}). 
             Both figures were generated from the same \texttt{Python} script in the \texttt{src/figures} directory (linked to in the \texttt{GitHub} icon in the margin).
-The other margin icon indicates that these figures depend on a dataset (a \texttt{.npz} file containing the posterior samples),
-            which is automatically generated by \showyourwork and uploaded to Zenodo.
+The other margin icon indicates that these figures depend on a dataset (a \texttt{.npz} file containing the posterior samples), which is automatically generated by \showyourwork and uploaded to Zenodo.
             Users wishing to reproduce the results in this paper can choose whether to re-generate this dataset or download a static version from Zenodo (linked to in the margin).
+            Figures adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
         }
@@
         \caption{
-            A static figure committed to the repository showing a total solar eclipse. 
-            Since this figure is in the \texttt{src/static} directory, \showyourwork knows not to attempt to generate it. 
+            A photograph taken during a total solar eclipse. 
+            Since this figure cannot be procedurally generated, we include it in the \texttt{src/static} directory, which tells \showyourwork to not attempt to generate it. 
             By default, margin icons are not added to static figures.
@@
 
+\bibliography{bib}
+
 \end{document}

### 2021-12-17 src/figures/HD118203.py

@@ -19,8 +19,8 @@ x_fold = (x - map_t0 + 0.5 * map_period) % map_period - 0.5 * map_period
 inds = np.argsort(x_fold)
 plt.scatter(x_fold, y - gp_pred - map_mean, c="k", s=3, alpha=0.5)
 plt.plot(x_fold[inds], lc_pred[inds] - map_mean, "C0")
-plt.xlabel("time since transit [days]", fontsize=12)
-plt.ylabel("relative flux [ppt]", fontsize=12)
+plt.xlabel("time since transit [days]", fontsize=16)
+plt.ylabel("relative flux [ppt]", fontsize=16)
 _ = plt.xlim(-0.25, 0.25)
 fig.savefig("HD118203_transit.pdf", bbox_inches="tight")
 
@@ -30,9 +30,9 @@ samples[:, 0] *= 1e5
 fig = corner.corner(
     samples,
     labels=[
-        "$\mathrm{period} - 6.13498$ [days]",
-        "planet/star radius ratio",
-        "impact parameter",
+        "$P - P_0$ [days]",
+        "radius ratio",
+        "impact param",
     ],
     truths=[0, 0.05538, 0.125],
 )
@@ -49,6 +49,6 @@ fig.axes[6].set_xticklabels(
 for axis in fig.axes:
     for tick in axis.xaxis.get_major_ticks() + axis.yaxis.get_major_ticks():
         tick.label.set_fontsize(6)
-    axis.set_xlabel(axis.get_xlabel(), fontsize=12)
-    axis.set_ylabel(axis.get_ylabel(), fontsize=12)
+    axis.set_xlabel(axis.get_xlabel(), fontsize=16)
+    axis.set_ylabel(axis.get_ylabel(), fontsize=16)
 fig.savefig("HD118203_corner.pdf", bbox_inches="tight")

### 2021-12-17 src/figures/luhman16b.py

@@ -1,0 +1,87 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pickle
+
+
+# Load the dataset
+with open("../data/luhman16b.pickle", "rb") as f:
+    data = pickle.load(f, encoding="latin1")
+
+# Timestamps (from Ian Crossfield)
+t = np.array(
+    [
+        0.0,
+        0.384384,
+        0.76825872,
+        1.15339656,
+        1.5380364,
+        1.92291888,
+        2.30729232,
+        2.69268336,
+        3.07654752,
+        3.46219464,
+        3.8473428,
+        4.23171624,
+        4.61583456,
+        4.99971048,
+    ]
+)
+
+# Use the first epoch's wavelength array
+lams = data["chiplams"][0]
+
+# Interpolate onto that array
+observed = np.empty((14, 4, 1024))
+template = np.empty((14, 4, 1024))
+broadened = np.empty((14, 4, 1024))
+for k in range(14):
+    for c in range(4):
+        observed[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["obs1"][k][c] / data["chipcors"][k][c],
+        )
+        template[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["chipmodnobroad"][k][c] / data["chipcors"][k][c],
+        )
+        broadened[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["chipmods"][k][c] / data["chipcors"][k][c],
+        )
+
+# Get the final data arrays
+wav = data["chiplams"][:, 2]
+flux = data["obs1"][:, 2] / data["chipcors"][:, 2]
+model = data["chipmods"][:, 2] / data["chipcors"][:, 2]
+
+# Plot the spectra
+fig, ax = plt.subplots(1, figsize=(8, 5))
+fig.subplots_adjust(wspace=0.1)
+for k in range(14):
+    ax.plot(wav[k], 0.65 * k + flux[k], "k.", ms=2, alpha=0.5, zorder=-1)
+    ax.plot(wav[k], 0.65 * k + model[k], "C1-", lw=1)
+
+# Appearance hacks
+ax.spines["left"].set_visible(False)
[…]

### 2021-12-17 src/figures/role_eccentricity.py

@@ -1,0 +1,151 @@
+"""
+This is the script that generates Figure 3 in Wagg et al. (2021).
+
+Original version:
+
+https://github.com/TeamLEGWORK/LEGWORK-paper/blob/d0afa5/src/figures/role_eccentricity.py
+
+Original caption:
+
+An illustration of the effect of eccentricity on the detectability 
+of a LISA source. The three sets of points are coloured by their 
+eccentricity and each individual point corresponds to a harmonic 
+frequency, where its height above the curve gives its SNR. We 
+annotate each set of points with its total SNR and overlay the 
+LISA sensitivity curve. The dotted vertical lines indicate the 
+frequency at which the ma- jority of the gravitational wave signal 
+is concentrated.
+
+"""
+
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+from astropy.visualization import quantity_support
+
+quantity_support()
+
+plt.rc("font", family="serif")
+plt.rcParams["text.usetex"] = False
+fs = 24
+
+# update various fontsizes to match
+params = {
+    "figure.figsize": (12, 8),
+    "legend.fontsize": fs,
+    "axes.labelsize": fs,
+    "xtick.labelsize": 0.9 * fs,
+    "ytick.labelsize": 0.9 * fs,
+    "axes.linewidth": 1.1,
+    "xtick.major.size": 7,
+    "xtick.minor.size": 4,
+    "ytick.major.size": 7,
+    "ytick.minor.size": 4,
+}
+plt.rcParams.update(params)
+
+# set eccentricities
+ecc = np.array([1e-6, 0.6, 0.9])
+n_binaries = len(ecc)
+
+# use constant values for mass, f_orb and distance
+m_1 = np.repeat(0.6, n_binaries) * u.Msun
+m_2 = np.repeat(0.6, n_binaries) * u.Msun
+f_orb = np.repeat(1.5e-3, n_binaries) * u.Hz
+dist = np.repeat(15, n_binaries) * u.kpc
+
+# get the SNR in each harmonic
+snr2_n = lw.snr.snr_ecc_evolving(
+    m_1=m_1,
+    m_2=m_2,
+    f_orb_i=f_orb,
+    ecc=ecc,
+    dist=dist,
+    harmonics_required=100,
+    t_obs=4 * u.yr,
[…]

### 2021-12-18 src/figures/dag.py
added DAG figure

@@ -1,0 +1,133 @@
+import graphviz
+from pathlib import Path
+import json
+import subprocess
+
+
+# Make sure we're running this from the workflow
+try:
+    snakemake
+except NameError:
+    raise Exception("This script must be run from within a Snakemake workflow.")
+
+# Node border colors
+colors = dict(
+    zenodo="#1f77b4",
+    analysis="black",
+    script="black",
+    figure="black",
+    dataset="#1f77b4",
+    other="black",
+    edge="black",
+)
+
+# Get figure metadata
+dependencies = snakemake.config.get("dependencies", {})
+zenodo = snakemake.config.get("zenodo", {})
+sandbox = snakemake.config.get("zenodo_sandbox", {})
+with open(".showyourwork/scripts.json", "r") as f:
+    script_info = json.load(f)
+
+# Instantiate the graph
+dot = graphviz.Digraph("dag", node_attr={"shape": "box", "penwidth": "2", "width": "1"})
+
+# Figures
+png_files = []
+for figure in script_info.get("figures", []):
+
+    # Get metadata for this figure
+    script = script_info["figures"][figure]["script"]
+    files = script_info["figures"][figure]["files"]
+
+    # Figure node
+    dot.node(script, label=script.replace("src/", ""), color=colors["script"])
+
+    # Loop through figure dependencies
+    for dependency in dependencies.get(script, []):
+        if not dependency.endswith(".zenodo"):
+
+            # Dependency node
+            if zenodo.get(dependency, {}) or sandbox.get(dependency, {}):
+                dot.node(
+                    dependency,
+                    label=dependency.replace("src/", ""),
+                    color=colors["dataset"],
+                    shape="box3d",
+                )
+            else:
+                dot.node(
+                    dependency,
+                    label=dependency.replace("src/", ""),
+                    color=colors["other"],
+                    style="rounded",
+                )
+
+            # Zenodo metadata for this dependency
+            for zenodo_info, zenodo_stem in zip(
+                [zenodo.get(dependency, {}), sandbox.get(dependency, {})],
+                ["10.5281", "10.5072"],
+            ):
+                if zenodo_info:
+
+                    # Zenodo node
+                    zenodo_id = zenodo_info["id"]
+                    doi = f"{zenodo_stem}/zenodo.{zenodo_id}"
+                    dot.node(
+                        doi,
+                        label=doi.replace("src/", ""),
+                        color=colors["zenodo"],
+                        shape="cylinder",
+                        height="0.75",
+                    )
[…]

### 2021-12-18 src/figures/eccentricity.py

@@ -148,4 +148,4 @@ ax.set_ylim(1e-20, 2e-18)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("role_eccentricity.pdf", format="pdf", bbox_inches="tight")
+plt.savefig("eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2021-12-18 src/figures/placeholder.py

@@ -1,0 +1,41 @@
+"""Plot a pretty fractal.
+
+This script plots the Mandelbrot set (mandelbrot.pdf).
+The code below was adapted from
+
+https://scipy-lectures.org/intro/numpy/auto_examples/plot_mandelbrot.html
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+from numpy import newaxis
+import copy
+
+
+def compute_mandelbrot(N_max, some_threshold, nx, ny):
+    x = np.linspace(-2, 1, nx)
+    y = np.linspace(-1.5, 1.5, ny)
+    c = x[:, newaxis] + 1j * y[newaxis, :]
+    z = c
+    with np.warnings.catch_warnings():
+        np.warnings.simplefilter("ignore")
+        for j in range(N_max):
+            z = z ** 2 + c
+        mandelbrot_set = abs(z) < some_threshold
+    return mandelbrot_set
+
+
+fig = plt.figure(figsize=(8, 8))
+mandelbrot_set = np.round(1 - compute_mandelbrot(500, 50.0, 601, 401))
+tab10 = copy.copy(plt.get_cmap("tab10"))
+tab10.set_over("w")
+plt.imshow(
+    mandelbrot_set.T,
+    extent=[-2, 1, -1.5, 1.5],
+    interpolation="nearest",
+    cmap=tab10,
+    vmin=0,
+    vmax=0.9,
+)
+plt.gca().axis("off")
+fig.savefig("placeholder.pdf", bbox_inches="tight")

### 2021-12-18 src/figures/dag.py
tweaks

@@ -100,6 +100,8 @@ for figure in script_info.get("figures", []):
     # Figure images
     for file in files:
 
+        # DOT can't render PDF images, so we need to use ImageMagick
+        # to temporarily convert them to PNG
         png_file = file.replace(".pdf", ".png")
         subprocess.call(["convert", file, png_file])
         png_files.append(png_file)

### 2021-12-18 src/figures/dag.py
custom DAG generation

@@ -1,135 +1,0 @@
-import graphviz
-from pathlib import Path
-import json
-import subprocess
-
-
-# Make sure we're running this from the workflow
-try:
-    snakemake
-except NameError:
-    raise Exception("This script must be run from within a Snakemake workflow.")
-
-# Node border colors
-colors = dict(
-    zenodo="#1f77b4",
-    analysis="black",
-    script="black",
-    figure="black",
-    dataset="#1f77b4",
-    other="black",
-    edge="black",
-)
-
-# Get figure metadata
-dependencies = snakemake.config.get("dependencies", {})
-zenodo = snakemake.config.get("zenodo", {})
-sandbox = snakemake.config.get("zenodo_sandbox", {})
-with open(".showyourwork/scripts.json", "r") as f:
-    script_info = json.load(f)
-
-# Instantiate the graph
-dot = graphviz.Digraph("dag", node_attr={"shape": "box", "penwidth": "2", "width": "1"})
-
-# Figures
-png_files = []
-for figure in script_info.get("figures", []):
-
-    # Get metadata for this figure
-    script = script_info["figures"][figure]["script"]
-    files = script_info["figures"][figure]["files"]
-
-    # Figure node
-    dot.node(script, label=script.replace("src/", ""), color=colors["script"])
-
-    # Loop through figure dependencies
-    for dependency in dependencies.get(script, []):
-        if not dependency.endswith(".zenodo"):
-
-            # Dependency node
-            if zenodo.get(dependency, {}) or sandbox.get(dependency, {}):
-                dot.node(
-                    dependency,
-                    label=dependency.replace("src/", ""),
-                    color=colors["dataset"],
-                    shape="box3d",
-                )
-            else:
-                dot.node(
-                    dependency,
-                    label=dependency.replace("src/", ""),
-                    color=colors["other"],
-                    style="rounded",
-                )
-
-            # Zenodo metadata for this dependency
-            for zenodo_info, zenodo_stem in zip(
-                [zenodo.get(dependency, {}), sandbox.get(dependency, {})],
-                ["10.5281", "10.5072"],
-            ):
-                if zenodo_info:
-
-                    # Zenodo node
-                    zenodo_id = zenodo_info["id"]
-                    doi = f"{zenodo_stem}/zenodo.{zenodo_id}"
-                    dot.node(
-                        doi,
-                        label=doi.replace("src/", ""),
-                        color=colors["zenodo"],
-                        shape="cylinder",
-                        height="0.75",
-                    )
[…]

### 2021-12-20 src/ms.tex
added DAG figure
tweaks
custom DAG generation
rossby ridge

@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/role_eccentricity.pdf}
+        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
         \caption{
@@
         }
-        \label{fig:role_eccentricity}
+        \label{fig:eccentricity}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
+        \caption{
+            Rossby ridge. Figure reproduced from David et al. (in prep).
+        }
+        \label{fig:rossbyridge}
     \end{centering}
@@
         \caption{
-            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}). 
+            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}); adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
             Both figures were generated from the same \texttt{Python} script in the \texttt{src/figures} directory (linked to in the \texttt{GitHub} icon in the margin).
@@
             Users wishing to reproduce the results in this paper can choose whether to re-generate this dataset or download a static version from Zenodo (linked to in the margin).
-            Figures adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
         }
@@
     \begin{centering}
-        \includegraphics[width=0.75\linewidth]{static/eclipse.jpeg}
+        \includegraphics[width=\linewidth]{static/TESSaperture.pdf}
         \caption{
-            A photograph taken during a total solar eclipse. 
-            Since this figure cannot be procedurally generated, we include it in the \texttt{src/static} directory, which tells \showyourwork to not attempt to generate it. 
+            \emph{TESS} target pixel file (TPF) of V1298 Tau
+            overlaid with an r-band sky image from the Digitized Sky Survey (DSS);
+            reproduced from Figure 1 in \citet{Feinstein2021}.
+            This figure exists as a static PDF, with no associated script to
+            generate it.
+            We therefore include it in the \texttt{src/static} directory, which tells \showyourwork to not attempt to generate it. 
             By default, margin icons are not added to static figures.
-            Here we manually add icons linking to the original photograph on Wikimedia Commons and its license using the \texttt{\textbackslash marginicon} command.
+            Here we manually add an icon linking to the original paper using the \texttt{\textbackslash marginicon} command.
         }
         \marginicon{%
-            \stackon[3pt]{%
-                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg}{\color{sywBlue}\faWikipediaW}%
-            }{%
-                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg\#Licensing}{\color{sywBlue}\faCreativeCommons}%
-            }%
+            \href{https://ui.adsabs.harvard.edu/abs/2021arXiv211108660F}{\color{sywBlue}\faNewspaper[regular]}
         }
@@
 
+\begin{figure*}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/dag.pdf}
+        \caption{
+            A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
+        }
+        \label{fig*:dag}
+    \end{centering}
+\end{figure*}
+
 \bibliography{bib}

### 2021-12-20 src/figures/helpers/sun.py

@@ -1,0 +1,17 @@
+#!/usr/bin/env python
+# coding: utf-8
+import numpy as np
+import astropy.constants as c
+
+
+__all__ = ["sun"]
+
+
+# Data for the Sun
+sun = {
+    "teff": 5772,
+    "prot": 25.4,
+    "e_prot": 25.4 - 24.5,
+    "E_prot": 36 - 25.4,
+    "logg": np.log10(c.GM_sun.cgs.value / c.R_sun.cgs.value ** 2),
+}

### 2021-12-20 src/figures/placeholder.py

@@ -1,41 +1,0 @@
-"""Plot a pretty fractal.
-
-This script plots the Mandelbrot set (mandelbrot.pdf).
-The code below was adapted from
-
-https://scipy-lectures.org/intro/numpy/auto_examples/plot_mandelbrot.html
-
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-from numpy import newaxis
-import copy
-
-
-def compute_mandelbrot(N_max, some_threshold, nx, ny):
-    x = np.linspace(-2, 1, nx)
-    y = np.linspace(-1.5, 1.5, ny)
-    c = x[:, newaxis] + 1j * y[newaxis, :]
-    z = c
-    with np.warnings.catch_warnings():
-        np.warnings.simplefilter("ignore")
-        for j in range(N_max):
-            z = z ** 2 + c
-        mandelbrot_set = abs(z) < some_threshold
-    return mandelbrot_set
-
-
-fig = plt.figure(figsize=(8, 8))
-mandelbrot_set = np.round(1 - compute_mandelbrot(500, 50.0, 601, 401))
-tab10 = copy.copy(plt.get_cmap("tab10"))
-tab10.set_over("w")
-plt.imshow(
-    mandelbrot_set.T,
-    extent=[-2, 1, -1.5, 1.5],
-    interpolation="nearest",
-    cmap=tab10,
-    vmin=0,
-    vmax=0.9,
-)
-plt.gca().axis("off")
-fig.savefig("placeholder.pdf", bbox_inches="tight")

### 2021-12-20 src/figures/rossbyridge.py

@@ -1,0 +1,43 @@
+#!/usr/bin/env python
+# coding: utf-8
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from helpers.sun import sun
+
+# McQuillan et al. 2014
+mcq = pd.read_csv("../data/McQuillan2014.csv")
+mcq = mcq.add_prefix("mcq_")
+
+# LAMOST-Kepler
+lam = pd.read_csv("../data/KeplerRot-LAMOST.csv")
+
+# Drop duplicate sources, keeping the one with the brighter G magnitude
+lam = lam.sort_values(["KIC", "Gmag"], ascending=(True, True))
+lam = lam.merge(mcq, how="left", left_on="KIC", right_on="mcq_KIC")
+lam = lam.drop_duplicates(subset=["KIC"], keep="first")
+lam_mask = lam["Teff_lam"] > 3000
+lam_mask = lam["Teff_lam"] < 8000
+lam_mask &= lam["logg_lam"] > 3
+lam_mask &= lam["logg_lam"] < 5
+lam_mask &= abs(lam["feh_lam"]) < 2
+lam = lam[lam_mask]
+
+# Plot
+fig, ax = plt.subplots(1, figsize=(4, 4))
+ax.scatter(lam["Teff_lam"], lam["mcq_Prot"], marker=".", rasterized=True, s=0.1)
+ax.set_xlabel("Effective temperature [K]")
+ax.set_xlim(7250, 3250)
+ax.set_ylim(-2, 60)
+ax.plot(sun["teff"], sun["prot"], "o", color="C1")
+ax.errorbar(
+    sun["teff"],
+    sun["prot"],
+    yerr=np.vstack([sun["e_prot"], sun["E_prot"]]),
+    fmt="o",
+    color="C1",
+    mec="white",
+    ms=6,
+)
+ax.set_ylabel("Rotation period [d]")
+fig.savefig("rossbyridge.pdf", bbox_inches="tight", dpi=100)

### 2021-12-20 src/ms.tex
working on paper

@@
 
-% Filler text
-\usepackage{blindtext}
+\usepackage{listings}
+
+\lstdefinestyle{LaTeX}{%
+    language=[LaTeX]TeX,
+    basicstyle=\ttfamily\footnotesize,
+    texcsstyle=*\bf\color{black},
+    numbers=none,
+    breaklines=true,
+    commentstyle=\color{red},
+    frame=single,
+    tabsize=2,
+    keywords={begin,caption,label,end,includegraphics},   
+}
 
@@
 \begin{abstract}
-    \blindtext
+    Abstract coming soon.
 \end{abstract}
@@
 
+Introduction coming soon.
+
+\section{Inferring the figure tree}
+
+\showyourwork determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file.
+Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
+Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
+%
+\begin{lstlisting}[
+    style=LaTeX,
+    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
+    emph={figures/eccentricity.pdf,fig:eccentricity},
+    emphstyle={\color{blue}}
+]
+\begin{figure}
+  \begin{centering}
+    \includegraphics{figures/eccentricity.pdf}
+    \caption{...}
+    \label{fig:eccentricity}
+  \end{centering}
+\end{figure}
+\end{lstlisting}
+
 \begin{figure}[ht!]
@@
         \caption{
-            LEGWORK plot. Figure reproduced from \citet{Wagg2021}.
+            The effect of eccentricity on the detectability of a \emph{LISA} source; reproduced from Figure 3 in \citet{Wagg2021}.
         }
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
+        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
         \caption{
-            Rossby ridge. Figure reproduced from David et al. (in prep).
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021}. 
+            Data originally from \citet{Crossfield2014}.
         }
-        \label{fig:rossbyridge}
+        \label{fig:luhman16b}
     \end{centering}
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
         \caption{
-            Caption. Figure adapted from \citet{Luger2021}; data originally from \citet{Crossfield2014}.
+            A pile-up of stars in the rotation period-temperature space at slightly faster rotation than the sun (orange dot); adapted from Figure 1 in David et al. (in prep).
         }
-        \label{fig:luhman16b}
+        \label{fig:rossbyridge}
     \end{centering}
@@
             A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
+            Figure scripts are represented by black rectangles; helper scripts (such as ones imported by figure scripts or used in dataset generation) are similar, but have rounded edges.
+            Blue cylinders correspond to Zenodo records; blue boxes correspond to datasets.
         }

### 2021-12-21 src/ms.tex
add dir tree

@@
 
+\lstdefinestyle{bash}{%
+    language=bash,
+    basicstyle=\ttfamily\footnotesize,
+    texcsstyle=*\bf\color{black},
+    numbers=none,
+    breaklines=true,
+    commentstyle=\color{red},
+    frame=single
+}
 \lstdefinestyle{LaTeX}{%
@@
 }
+\definecolor{lsthilite}{rgb}{0.0,0.0,1.0}
 
@@
 
-\section{Inferring the figure tree}
+\section{Repository structure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=0.5\linewidth]{figures/tree.pdf}
+        \caption{
+            Basic repository structure for an open source scientfic article.
+        }
+        \label{fig:tree}
+    \end{centering}
+\end{figure}
+
+See Figure~\ref{fig:tree}.
+
+\section{Automatic figure generation}
 
@@
     emph={figures/eccentricity.pdf,fig:eccentricity},
-    emphstyle={\color{blue}}
+    emphstyle={\color{lsthilite}}
 ]
@@
 \end{lstlisting}
+%
+The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
+Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which can be executed to produce that figure.
+By default, figure scripts are expected to be \texttt{Python} scripts, so in this case \showyourwork will attempt to run
+%
+\begin{lstlisting}[
+    style=bash
+]
+python eccentricity.py
+\end{lstlisting}
+%
+from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
 

### 2021-12-21 src/ms.tex
more text

@@
 
-\usepackage{listings}
-
-\lstdefinestyle{bash}{%
-    language=bash,
-    basicstyle=\ttfamily\footnotesize,
-    texcsstyle=*\bf\color{black},
-    numbers=none,
-    breaklines=true,
-    commentstyle=\color{red},
-    frame=single
-}
-\lstdefinestyle{LaTeX}{%
-    language=[LaTeX]TeX,
-    basicstyle=\ttfamily\footnotesize,
-    texcsstyle=*\bf\color{black},
-    numbers=none,
-    breaklines=true,
-    commentstyle=\color{red},
-    frame=single,
-    tabsize=2,
-    keywords={begin,caption,label,end,includegraphics},   
-}
-\definecolor{lsthilite}{rgb}{0.0,0.0,1.0}
+% Custom style defs for this paper
+\input{style.tex}
 
@@
 
+\section{Starting a project}
+\label{sec:start}
+%
+Users can start a new project by \href{https://github.com/rodluger/showyourwork-template/generate}{creating a fresh repository based on the \texttt{showyourwork-template}}.
+This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process.
+After a few minutes...
+%
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{static/banner.png}
+        \caption{
+            The default \texttt{README} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
+        }
+        \label{fig:banner}
+    \end{centering}
+\end{figure}
+%
+
 \section{Repository structure}
-
+\label{sec:struct}
+%
 \begin{figure}[ht!]
@@
         \caption{
-            Basic repository structure for an open source scientfic article.
+            The basic repository structure for an open source scientfic article based on \texttt{showyourwork-template}.
+            See text for details.
         }
@@
 \end{figure}
-
-See Figure~\ref{fig:tree}.
+%
+Figure~\ref{fig:tree} shows the basic directory structure for a repository instantiated from \texttt{showyourwork-template}. 
+The main components are:
+\begin{itemize}
+    \item \texttt{.github/workflow/showyourwork.yml}: The configuration file for the \texttt{GitHub Actions} workflow, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
+    \item \texttt{showyourwork}: The \texttt{git} submodule containing the \showyourwork workflow, which manages the entire build process for the article.
+    \item \texttt{src}: A directory containing all of the scripts needed to generate the article.
+    \item \texttt{src/data}: A directory containing programmatically generated (or downloaded) datasets and dependencies that are not tracked by \texttt{git}; this directory should be empty when the repository is first cloned.
+    \item \texttt{src/figures}: A directory containing all of the scripts needed to generate the article figures.
+    When the article is built, figure (output) files will be stored here, but they should not be tracked by \texttt{git}.
+    \item \texttt{src/static}: A directory containing miscellaneous files (usually figures) that are tracked by \texttt{git}.
+    These may include photographs, flowcharts, or other figures that cannot be programmatically generated.
+    \item \texttt{src/ms.tex}: The main \texttt{TeX} article manuscript.
+    \item \texttt{Makefile}: A read-only UNIX/Linux makefile that enables users to build the article by running \texttt{make} in the command-line terminal.
+    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow.
+    By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
+    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow.
+    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}, etc.
+\end{itemize}
 
 \section{Automatic figure generation}
-
-\showyourwork determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file.
+\label{sec:auto-fig}
+%
+The workflow automatically determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file.
 Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
@@
 The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
-Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which can be executed to produce that figure.
-By default, figure scripts are expected to be \texttt{Python} scripts, so in this case \showyourwork will attempt to run
+Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which should be executed to produce that figure.
+By default, figure scripts are expected to be \texttt{Python} scripts, so in this case the workflow will attempt to run
 %
@@
 from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
+
+This behavior may be customized in several ways. 
+First, the figure script need not be a \texttt{Python} script; see \S\ref{sec:other-lang} for information on how to include scripts in any language.
+Second, a common scenario involves a script that generates multiple figures.
+These can all be included (using \texttt{includegraphics}) in the same figure environment with a single shared label (denoting the name of the script)
+...
+
+\section{Support for other languages}
+\label{sec:other-lang}
+%
+Scripts in languages other than \texttt{Python} are supported via the inclusion of entries under the \texttt{scripts} key in the \texttt{showyourwork.yml} config file. 
+Consider Figure~\ref{fig:tree}, which was generated from the \texttt{TeX} file \texttt{figures/tree.tex}, which contains a \texttt{TikZ} picture. 
+In the main manuscript, we include the figure in the usual way, i.e.,
+%
+\begin{lstlisting}[
+    style=LaTeX,
+    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
+    emph={figures/eccentricity.pdf,fig:eccentricity},
+    emphstyle={\color{lsthilite}}
+]
+\begin{figure}
+  \begin{centering}
+    \includegraphics{figures/tree.pdf}
+    \caption{...}
+    \label{fig:tree}
+  \end{centering}
+\end{figure}
+\end{lstlisting}
+%
+By default, as we saw in \S\ref{sec:auto-fig}, this instructs the workflow to execute a file called \texttt{figures/tree.py} to generate the corresponding figure. 
+However, in the present case, that file does not exist; instead, we have a file called \texttt{figures/tree.tex}, which we would like to compile into a \texttt{PDF} using te \texttt{tectonic} engine.
+We can instruct the workflow to do this by specifying the following in \texttt{showyourwork.yml}:
+%
+\begin{lstlisting}[
+    style=yaml,
+    otherkeywords={script.path,script.name},
+    emph={script.path,script.name},
+    emphstyle={\color{lsthilite}}
+]
+scripts:
+  tex:
+    cd {script.path} && tectonic {script.name}
+\end{lstlisting}
+%
+Each entry under the \texttt{scripts} key should be a file extension, and under each one, a string containing a shell command that instructs the workflow how to execute a given {\color{lsthilite}\texttt{script}} to produce a given {\color{lsthilite}\texttt{output}}.
+For convenience, the following placeholders are recognized and expand as follows at runtime:
+%
+\begin{itemize}
+\item \texttt{\{script\}}: The full path to the input script.
+\item \texttt{\{script.path\}}: The full path to the directory containing the input script.
+\item \texttt{\{script.name\}}: The name of the input script (without the path).
+\item \texttt{\{output\}}: The full path to the output file.
+\item \texttt{\{output.path\}}: The full path to the directory containing the output file.
+\item \texttt{\{output.name\}}: The name of the output file (without the path).
+\end{itemize}
+%
+If additional customization is needed, such as the need to provide command-line arguments that are specific to individual figures, users should instead provide custom rules in the \texttt{Snakefile} (\S\ref{sec:arbitrary-rules}).
+
+\section{Arbitrary rules}
+\label{sec:arbitrary-rules}
+%
+Coming soon.
 

### 2021-12-21 src/ms.tex
more words

@@
 \author[0000-0002-0296-3826]{Rodrigo Luger}
+\author{Others TBD}
 
@@
 
+\section{Prerequisites}
+\label{sec:prereq}
+Conda. Linux/UNIX/Mac. GitHub account.
+
 \section{Starting a project}
@@
 Users can start a new project by \href{https://github.com/rodluger/showyourwork-template/generate}{creating a fresh repository based on the \texttt{showyourwork-template}}.
-This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process.
-After a few minutes...
+This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process and build a skeleton version of the paper.
+After a few minutes, a banner will appear on the repository's main page with links to the build logs and the compiled article PDF (see Figure~\ref{fig:banner}).
 %
-\begin{figure}[ht!]
+\begin{figure}[th!]
     \begin{centering}
@@
         \caption{
-            The default \texttt{README} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
+            The default \texttt{README.md} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
         }
@@
 %
+At this point, the repository can be cloned locally, e.g.,
+%
+\begin{lstlisting}[
+    style=bash,
+    otherkeywords={user,repo},
+    emph={user,repo},
+    emphstyle={\color{lsthilite}}
+]
+git clone https://github.com/user/repo
+cd repo
+\end{lstlisting}
+%
+where {\color{lsthilite}\texttt{user}} and {\color{lsthilite}\texttt{repo}} are the \texttt{GitHub} user name and repository name, respectively.
+The user may now edit the manuscript (\texttt{src/ms.tex}), add figure scripts to the \texttt{src/figures} directory, etc. (see \S\ref{sec:struct}).
+The article may be built locally by running \texttt{make} in the top level directory (see \S\ref{sec:local-builds}).
+Upon committing and pushing the changes to the remote repository, the \texttt{GitHub Action} will be triggered automatically, generating a new article PDF in sync with the latest changes (see \S\ref{sec:remote-builds}).
+
+\section{Reproducing a project}
+\label{sec:reproduce}
+%
+Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{make}:
+%
+\begin{lstlisting}[
+    style=bash,
+    otherkeywords={user,repo},
+    emph={user,repo},
+    emphstyle={\color{lsthilite}}
+]
+git clone https://github.com/user/repo
+cd repo
+make
+\end{lstlisting}
+%
+This will create a fresh \texttt{conda} environment and run the \texttt{Snakemake} workflow to build the article from scratch, which may entail the execution of computationally-intensive scripts/tasks.
+These may sometimes be skipped by instead running
+%
+\begin{lstlisting}[
+    style=bash
+]
+make fast
+\end{lstlisting}
+%
+which will download any available intermediate files from \texttt{Zenodo} instead of generating them from scratch. See \S\ref{sec:local-builds} for details.
+
+\section{Local builds}
+\label{sec:local-builds}
+%
+Coming soon.
+
+\section{Remote builds}
+\label{sec:remote-builds}
+%
+Coming soon.
 

### 2021-12-21 src/ms.tex
words

@@
         \caption{
-            The basic repository structure for an open source scientfic article based on \texttt{showyourwork-template}.
+            The basic repository structure for an open source scientific article based on \texttt{showyourwork-template}.
             See text for details.
@@
     \item \texttt{.github/workflow/showyourwork.yml}: The configuration file for the \texttt{GitHub Actions} workflow, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
-    \item \texttt{showyourwork}: The \texttt{git} submodule containing the \showyourwork workflow, which manages the entire build process for the article.
+    \item \texttt{showyourwork}: The \texttt{git} submodule containing the main workflow, which manages the entire build process for the article.
     \item \texttt{src}: A directory containing all of the scripts needed to generate the article.
@@
     \item \texttt{Makefile}: A read-only UNIX/Linux makefile that enables users to build the article by running \texttt{make} in the command-line terminal.
-    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow.
+    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow; see \S\ref{sec:Snakefile}
     By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
-    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow.
-    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}, etc.
+    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow; see \S\ref{sec:environmentyml}
+    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}, etc.; see \S\ref{sec:showyourworkyml}
 \end{itemize}
@@
 
-\begin{figure*}[ht!]
+\section{This paper}
+
+\begin{figure*}[p!]
     \begin{centering}
@@
 
+\subsection{The \texttt{Snakefile}}
+\label{sec:Snakefile}
+%
+\lstinputlisting[
+    style=Snakefile
+]
+{../Snakefile}
+
+\subsection{The \texttt{showyourwork.yml} file}
+\label{sec:showyourworkyml}
+%
+\lstinputlisting[
+    style=yaml
+]
+{../showyourwork.yml}
+
+\subsection{The \texttt{environment.yml} file}
+\label{sec:environmentyml}
+%
+\lstinputlisting[
+    style=yaml
+]
+{../environment.yml}
+
 \bibliography{bib}

### 2021-12-21 src/ms.tex
words, pictures

@@
 \section{Introduction}
+\label{sec:intro}
 
 Introduction coming soon.
+
+\section{Examples}
+\label{sec:examples}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
+        \caption{
+            The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2021}. 
+            This figure was automatically generated from the script \texttt{src/figures/eccentricity.py}.
+        }
+        \label{fig:eccentricity}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+        \caption{
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+            This figure was automatically generated from the script \texttt{src/figures/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
+        }
+        \label{fig:luhman16b}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
+        \caption{
+            A pile-up of stars in the rotation period-temperature space at slightly faster rotation than the Sun (orange dot); adapted from Figure 1 in David et al. (in prep).
+            This figure was automatically generated from the script \texttt{src/figures/rossbyridge.py}, a dataset downloaded from \texttt{Zenodo}, and the helper script \texttt{src/figures/helpers/sun.py}.
+        }
+        \label{fig:rossbyridge}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/HD118203_transit.pdf}
+        \includegraphics[width=\linewidth]{figures/HD118203_corner.pdf}
+        \caption{
+            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}); adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
+            Both figures were generated from the script \texttt{src/figures/HD118203.py}. 
+            They both depend on an intermediate result (a dataset containing the MCMC posterior samples), which can either be generated from scratch by running \texttt{src/analysis/HD118203.py} or by downloading a cached version from \texttt{Zenodo}.
+        }
+        \label{fig:HD118203}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{static/TESSaperture.pdf}
+        \caption{
+            \emph{TESS} target pixel file (TPF) of V1298 Tau
+            overlaid with an r-band sky image from the Digitized Sky Survey (DSS);
+            reproduced from Figure 1 in \citet{Feinstein2021}.
+            This figure exists as a static PDF, with no associated script to
+            generate it.
+            We therefore include it in the \texttt{src/static} directory, which tells the workflow to not attempt to generate it. 
+            By default, margin icons are not added to static figures.
+            Here we manually add an icon linking to the original paper using the \texttt{\textbackslash marginicon} command.
+        }
+        \marginicon{%
+            \href{https://ui.adsabs.harvard.edu/abs/2021arXiv211108660F}{\color{sywBlue}\faNewspaper[regular]}
+        }
+        \label{fig:eclipse}
+    \end{centering}
+\end{figure}
 
@@
 Second, a common scenario involves a script that generates multiple figures.
-These can all be included (using \texttt{includegraphics}) in the same figure environment with a single shared label (denoting the name of the script)
+These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script)
 ...
@@
 
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
-        \caption{
-            The effect of eccentricity on the detectability of a \emph{LISA} source; reproduced from Figure 3 in \citet{Wagg2021}.
-        }
-        \label{fig:eccentricity}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
-        \caption{
-            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021}. 
-            Data originally from \citet{Crossfield2014}.
-        }
-        \label{fig:luhman16b}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
-        \caption{
-            A pile-up of stars in the rotation period-temperature space at slightly faster rotation than the sun (orange dot); adapted from Figure 1 in David et al. (in prep).
-        }
-        \label{fig:rossbyridge}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/HD118203_transit.pdf}
-        \includegraphics[width=\linewidth]{figures/HD118203_corner.pdf}
-        \caption{
-            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}); adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
-            Both figures were generated from the same \texttt{Python} script in the \texttt{src/figures} directory (linked to in the \texttt{GitHub} icon in the margin).
-The other margin icon indicates that these figures depend on a dataset (a \texttt{.npz} file containing the posterior samples), which is automatically generated by \showyourwork and uploaded to Zenodo.
-            Users wishing to reproduce the results in this paper can choose whether to re-generate this dataset or download a static version from Zenodo (linked to in the margin).
-        }
-        \label{fig:HD118203}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{static/TESSaperture.pdf}
-        \caption{
-            \emph{TESS} target pixel file (TPF) of V1298 Tau
-            overlaid with an r-band sky image from the Digitized Sky Survey (DSS);
-            reproduced from Figure 1 in \citet{Feinstein2021}.
-            This figure exists as a static PDF, with no associated script to
-            generate it.
-            We therefore include it in the \texttt{src/static} directory, which tells \showyourwork to not attempt to generate it. 
-            By default, margin icons are not added to static figures.
-            Here we manually add an icon linking to the original paper using the \texttt{\textbackslash marginicon} command.
-        }
-        \marginicon{%
-            \href{https://ui.adsabs.harvard.edu/abs/2021arXiv211108660F}{\color{sywBlue}\faNewspaper[regular]}
-        }
-        \label{fig:eclipse}
-    \end{centering}
-\end{figure}
-
 \section{This paper}

### 2021-12-23 src/ms.tex
misc

@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{static/TESSaperture.pdf}
+        \includegraphics[width=\linewidth]{figures/v1298tau.pdf}
         \caption{
@@
             reproduced from Figure 1 in \citet{Feinstein2021}.
-            This figure exists as a static PDF, with no associated script to
-            generate it.
-            We therefore include it in the \texttt{src/static} directory, which tells the workflow to not attempt to generate it. 
-            By default, margin icons are not added to static figures.
-            Here we manually add an icon linking to the original paper using the \texttt{\textbackslash marginicon} command.
+            This figure was downloaded directly from the \texttt{GitHub} repository for that paper by providing a custom rule in the \texttt{Snakefile}.
+            By default, margin icons are not added to figures with custom rules.
+            Here we manually add an icon linking to the original figure using the \texttt{\textbackslash marginicon} command.
         }
         \marginicon{%
-            \href{https://ui.adsabs.harvard.edu/abs/2021arXiv211108660F}{\color{sywBlue}\faNewspaper[regular]}
+            \href{https://github.com/afeinstein20/v1298tau_tess/raw/c670e0/src/static/TESSaperture.pdf}{\color{sywBlue}\faFileImage}
         }
-        \label{fig:eclipse}
+        \label{fig*:v1298tau}
     \end{centering}
@@
             The default \texttt{README.md} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
+            Note that since this figure is a screenshot, we place it in the \texttt{src/static} folder and \texttt{git}-commit it.
+            The workflow skips the generation step for any figures in that directory; note the absence of a margin icon next to this caption.
         }
@@
 This behavior may be customized in several ways. 
-First, the figure script need not be a \texttt{Python} script; see \S\ref{sec:other-lang} for information on how to include scripts in any language.
-Second, a common scenario involves a script that generates multiple figures.
-These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script)
-...
+For instance, the figure script need not be a \texttt{Python} script; see \S\ref{sec:other-lang} for information on how to include scripts in any language.
+Another common scenario involves a script that generates multiple figures.
+These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script), or in multiple different figure environments by appending an arbitrary suffix to each figure label to make them all unique (i.e., \texttt{fig:eccentricity:one}, \texttt{fig:eccentricity:two}, etc.)
+And finally, this behavior may be overridden entirely by supplying a label that does not begin with \texttt{fig:}, in which case the workflow will not attempt to programmatically generate the figure.
+In this case, the figure must either be directly committed to the repository as a static figure (e.g., Figure~\ref{fig:banner}) or a custom rule must be provided in the \texttt{Snakefile} to generate it (e.g., Figure~\ref{fig*:v1298tau}).
 

### 2021-12-23 src/ms.tex
tweaks

@@
 These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script), or in multiple different figure environments by appending an arbitrary suffix to each figure label to make them all unique (i.e., \texttt{fig:eccentricity:one}, \texttt{fig:eccentricity:two}, etc.)
-And finally, this behavior may be overridden entirely by supplying a label that does not begin with \texttt{fig:}, in which case the workflow will not attempt to programmatically generate the figure.
-In this case, the figure must either be directly committed to the repository as a static figure (e.g., Figure~\ref{fig:banner}) or a custom rule must be provided in the \texttt{Snakefile} to generate it (e.g., Figure~\ref{fig*:v1298tau}).
+And finally, this behavior may be overridden entirely by either placing the figure in the \texttt{src/static} directory (and committing it directly to the \texttt{GitHub} repository) or by supplying a label that instead begins with \texttt{fig*:}, which instructs the workflow to not attempt to programmatically generate the figure.
+In the latter case, a custom rule must be provided in the \texttt{Snakefile} to generate it (see, e.g., Figure~\ref{fig*:v1298tau}).
 

### 2021-12-23 src/ms.tex
misc tweaks

@@
 %
-At this point, the repository can be cloned locally, e.g.,
-%
+At this point, the repository can be cloned locally, e.g.,\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-where {\color{lsthilite}\texttt{user}} and {\color{lsthilite}\texttt{repo}} are the \texttt{GitHub} user name and repository name, respectively.
+\end{minipage}
+
+\noindent where {\color{lsthilite}\texttt{user}} and {\color{lsthilite}\texttt{repo}} are the \texttt{GitHub} user name and repository name, respectively.
 The user may now edit the manuscript (\texttt{src/ms.tex}), add figure scripts to the \texttt{src/figures} directory, etc. (see \S\ref{sec:struct}).
@@
 %
-Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{make}:
-%
+Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{make}:\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-This will create a fresh \texttt{conda} environment and run the \texttt{Snakemake} workflow to build the article from scratch, which may entail the execution of computationally-intensive scripts/tasks.
-These may sometimes be skipped by instead running
-%
+\end{minipage}
+
+\noindent This will create a fresh \texttt{conda} environment and run the \texttt{Snakemake} workflow to build the article from scratch, which may entail the execution of computationally-intensive scripts/tasks.
+These may sometimes be skipped by instead running\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-which will download any available intermediate files from \texttt{Zenodo} instead of generating them from scratch. See \S\ref{sec:local-builds} for details.
+\end{minipage}
+
+\noindent which will download any available intermediate files from \texttt{Zenodo} instead of generating them from scratch. See \S\ref{sec:local-builds} for details.
 
@@
 Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
-Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
-%
+Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
+\end{minipage}
+
+\noindent The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
 Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which should be executed to produce that figure.
-By default, figure scripts are expected to be \texttt{Python} scripts, so in this case the workflow will attempt to run
-%
+By default, figure scripts are expected to be \texttt{Python} scripts, so in this case the workflow will attempt to run\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
+\end{minipage}
+
+\noindent from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
 
@@
 Consider Figure~\ref{fig:tree}, which was generated from the \texttt{TeX} file \texttt{figures/tree.tex}, which contains a \texttt{TikZ} picture. 
-In the main manuscript, we include the figure in the usual way, i.e.,
-%
+In the main manuscript, we include the figure in the usual way, i.e.,\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-By default, as we saw in \S\ref{sec:auto-fig}, this instructs the workflow to execute a file called \texttt{figures/tree.py} to generate the corresponding figure. 
+\end{minipage}
+
+\noindent By default, as we saw in \S\ref{sec:auto-fig}, this instructs the workflow to execute a file called \texttt{figures/tree.py} to generate the corresponding figure. 
 However, in the present case, that file does not exist; instead, we have a file called \texttt{figures/tree.tex}, which we would like to compile into a \texttt{PDF} using te \texttt{tectonic} engine.
-We can instruct the workflow to do this by specifying the following in \texttt{showyourwork.yml}:
-%
+We can instruct the workflow to do this by specifying the following in \texttt{showyourwork.yml}:\\
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[
@@
 \end{lstlisting}
-%
-Each entry under the \texttt{scripts} key should be a file extension, and under each one, a string containing a shell command that instructs the workflow how to execute a given {\color{lsthilite}\texttt{script}} to produce a given {\color{lsthilite}\texttt{output}}.
+\end{minipage}
+
+\noindent Each entry under the \texttt{scripts} key should be a file extension, and under each one, a string containing a shell command that instructs the workflow how to execute a given {\color{lsthilite}\texttt{script}} to produce a given {\color{lsthilite}\texttt{output}}.
 For convenience, the following placeholders are recognized and expand as follows at runtime:
@@
 \label{sec:arbitrary-rules}
+%
+Coming soon.
+
+\section{Zenodo interface}
+\label{sec:zenodo}
 %
@@
 %
+\begin{minipage}{\linewidth}
 \lstinputlisting[
@@
 {../Snakefile}
+\end{minipage}
 
@@
 {../showyourwork.yml}
+\end{minipage}
 
@@
 {../environment.yml}
+\end{minipage}
 

### 2021-12-23 src/ms.tex
intro

@@
 \input{style.tex}
+
+\usepackage{enumitem}
+\setlist[enumerate]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
+\setlist[itemize]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
 
@@
 
-Introduction coming soon.
+This paper introduces \showyourwork, a workflow that enables the creation and distribution of fully reproducible and open source scientific articles. 
+As astronomical software becomes increasingly more complex, and as research results become increasingly more interdependent, it is crucial to ensure the validity and correctness of papers published in the field.
+However, the current peer review system is simply not set up to do this, since checking all of the results in a paper would require the painstaking and methodical review of all of the paper's methods—which usually means scrutinizing all of the code used to generate the figures, tables, and other quantities in the paper.
+In practice, this is virtually impossible for three reasons:
+
+\begin{enumerate}
+    %
+    \item Modern codebases can be very large and often require deep familiarity with the software to use—not to mention review them.
+    %
+    \item  Writing a paper in astronomy is rarely ever done in a linear, procedural fashion: the codebase is constantly changing, and the state of the code when (say) Figure 1 was produced may be very different from that when (say) Figure 2 was made.
+    Moreover, many results depend on the execution of lengthy pipelines with intermediate steps, each potentially requiring manual tinkering that is not always documented and may be difficult to exactly replicate.
+    %
+    \item The majority of astronomical code is not open source and simply cannot be vetted by third parties. 
+    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., astropy, exoplanet, emcee, exofast...), most code associated with the generation of the results in individual papers is not open source; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
+    Even when the code is made publicly available, e.g., by being published on \texttt{GitHub}, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
+    And even with proper documentation, the code may require external dependencies, custom virtual environments, or access to closed-source datasets that make it difficult or impossible for a third party to replicate it.
+    %
+\end{enumerate}
+
+\showyourwork was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy. 
+It exists as a \texttt{GitHub} template repository, which can be cloned at the click of a button to set up a new article. 
+Users then add their LaTeX manuscript, bibliography, scripts used in the generation of the paper's figures, an anaconda environment specification, and instructions on how to download any external datasets required by the figures.
+Every time the user pushes a new commit to \texttt{GitHub}, the article is automatically built on the cloud using \texttt{GitHub Actions} and the resulting PDF is pushed to a separate branch of the repository.
+The build step—which sets up the conda environment, generates all figures from scratch (with intelligent caching), and compiles the PDF—acts as a unit test for the paper. 
+If it passes, the paper is (by definition) reproducible.
+
+The workflow works out of the box for simple projects, in which each figure is generated by running a given \texttt{Python} script. 
+But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations on clusters. 
+The workflow interfaces directly with \texttt{Zenodo}, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
+In fact, most of the stuff under the hood is there to make the workflow as flexible and customizable as possible; see the documentation for a list of examples of custom workflows.
+
+Papers that use this workflow can be reproduced by cloning the repository and running \texttt{make}. 
+Furthermore, these papers include clickable icons next to each of their figures linking to (1) the exact version of the script used to generate them and (2) the exact version(s) of the \texttt{Zenodo}-hosted dataset(s) used in their creation.
 

### 2022-01-12 src/tex/ms.tex
starting from scratch

--- 2021-12-23 src/ms.tex
@@
 \documentclass[twocolumn]{aastex631}
-
-% Custom style defs for this paper
-\input{style.tex}
 
@@
 
-Introduction coming soon.
-
-\section{Examples}
-\label{sec:examples}
-
 \begin{figure}[ht!]
@@
 
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
-        \caption{
-            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
-            This figure was automatically generated from the script \texttt{src/figures/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
-        }
-        \label{fig:luhman16b}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
-        \caption{
-            A pile-up of stars in the rotation period-temperature space at slightly faster rotation than the Sun (orange dot); adapted from Figure 1 in David et al. (in prep).
-            This figure was automatically generated from the script \texttt{src/figures/rossbyridge.py}, a dataset downloaded from \texttt{Zenodo}, and the helper script \texttt{src/figures/helpers/sun.py}.
-        }
-        \label{fig:rossbyridge}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/HD118203_transit.pdf}
-        \includegraphics[width=\linewidth]{figures/HD118203_corner.pdf}
-        \caption{
-            The phase-folded transit of HD 118203b in \emph{TESS} (\emph{top}) and the inferred joint posterior distributions over its period, radius, and impact parameter (\emph{bottom}); adapted from the \texttt{exoplanet} documentation \citep{ForemanMackey2021}.
-            Both figures were generated from the script \texttt{src/figures/HD118203.py}. 
-            They both depend on an intermediate result (a dataset containing the MCMC posterior samples), which can either be generated from scratch by running \texttt{src/analysis/HD118203.py} or by downloading a cached version from \texttt{Zenodo}.
-        }
-        \label{fig:HD118203}
-    \end{centering}
-\end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/v1298tau.pdf}
-        \caption{
-            \emph{TESS} target pixel file (TPF) of V1298 Tau
-            overlaid with an r-band sky image from the Digitized Sky Survey (DSS);
-            reproduced from Figure 1 in \citet{Feinstein2021}.
-            This figure was downloaded directly from the \texttt{GitHub} repository for that paper by providing a custom rule in the \texttt{Snakefile}.
-            By default, margin icons are not added to figures with custom rules.
-            Here we manually add an icon linking to the original figure using the \texttt{\textbackslash marginicon} command.
-        }
-        \marginicon{%
-            \href{https://github.com/afeinstein20/v1298tau_tess/raw/c670e0/src/static/TESSaperture.pdf}{\color{sywBlue}\faFileImage}
-        }
-        \label{fig*:v1298tau}
-    \end{centering}
-\end{figure}
-
-\section{Prerequisites}
-\label{sec:prereq}
-Conda. Linux/UNIX/Mac. GitHub account.
-
-\section{Starting a project}
-\label{sec:start}
-%
-Users can start a new project by \href{https://github.com/rodluger/showyourwork-template/generate}{creating a fresh repository based on the \texttt{showyourwork-template}}.
-This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process and build a skeleton version of the paper.
-After a few minutes, a banner will appear on the repository's main page with links to the build logs and the compiled article PDF (see Figure~\ref{fig:banner}).
-%
 \begin{figure}[th!]
     \begin{centering}
-        \includegraphics[width=\linewidth]{static/banner.png}
+        \includegraphics[width=\linewidth]{figures/banner.png}
         \caption{
@@
 \end{figure}
-%
-At this point, the repository can be cloned locally, e.g.,
-%
-\begin{lstlisting}[
-    style=bash,
-    otherkeywords={user,repo},
-    emph={user,repo},
-    emphstyle={\color{lsthilite}}
-]
-git clone https://github.com/user/repo
-cd repo
-\end{lstlisting}
-%
-where {\color{lsthilite}\texttt{user}} and {\color{lsthilite}\texttt{repo}} are the \texttt{GitHub} user name and repository name, respectively.
-The user may now edit the manuscript (\texttt{src/ms.tex}), add figure scripts to the \texttt{src/figures} directory, etc. (see \S\ref{sec:struct}).
-The article may be built locally by running \texttt{make} in the top level directory (see \S\ref{sec:local-builds}).
-Upon committing and pushing the changes to the remote repository, the \texttt{GitHub Action} will be triggered automatically, generating a new article PDF in sync with the latest changes (see \S\ref{sec:remote-builds}).
-
-\section{Reproducing a project}
-\label{sec:reproduce}
-%
-Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{make}:
-%
-\begin{lstlisting}[
-    style=bash,
-    otherkeywords={user,repo},
-    emph={user,repo},
-    emphstyle={\color{lsthilite}}
-]
-git clone https://github.com/user/repo
-cd repo
-make
-\end{lstlisting}
-%
-This will create a fresh \texttt{conda} environment and run the \texttt{Snakemake} workflow to build the article from scratch, which may entail the execution of computationally-intensive scripts/tasks.
-These may sometimes be skipped by instead running
-%
-\begin{lstlisting}[
-    style=bash
-]
-make fast
-\end{lstlisting}
-%
-which will download any available intermediate files from \texttt{Zenodo} instead of generating them from scratch. See \S\ref{sec:local-builds} for details.
-
-\section{Local builds}
-\label{sec:local-builds}
-%
-Coming soon.
-
-\section{Remote builds}
-\label{sec:remote-builds}
-%
-Coming soon.
-
-\section{Repository structure}
-\label{sec:struct}
-%
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=0.5\linewidth]{figures/tree.pdf}
-        \caption{
-            The basic repository structure for an open source scientific article based on \texttt{showyourwork-template}.
-            See text for details.
-        }
-        \label{fig:tree}
-    \end{centering}
-\end{figure}
-%
-Figure~\ref{fig:tree} shows the basic directory structure for a repository instantiated from \texttt{showyourwork-template}. 
-The main components are:
-\begin{itemize}
-    \item \texttt{.github/workflow/showyourwork.yml}: The configuration file for the \texttt{GitHub Actions} workflow, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
-    \item \texttt{showyourwork}: The \texttt{git} submodule containing the main workflow, which manages the entire build process for the article.
-    \item \texttt{src}: A directory containing all of the scripts needed to generate the article.
-    \item \texttt{src/data}: A directory containing programmatically generated (or downloaded) datasets and dependencies that are not tracked by \texttt{git}; this directory should be empty when the repository is first cloned.
-    \item \texttt{src/figures}: A directory containing all of the scripts needed to generate the article figures.
-    When the article is built, figure (output) files will be stored here, but they should not be tracked by \texttt{git}.
-    \item \texttt{src/static}: A directory containing miscellaneous files (usually figures) that are tracked by \texttt{git}.
-    These may include photographs, flowcharts, or other figures that cannot be programmatically generated.
-    \item \texttt{src/ms.tex}: The main \texttt{TeX} article manuscript.
-    \item \texttt{Makefile}: A read-only UNIX/Linux makefile that enables users to build the article by running \texttt{make} in the command-line terminal.
-    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow; see \S\ref{sec:Snakefile}
-    By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
-    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow; see \S\ref{sec:environmentyml}
-    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}, etc.; see \S\ref{sec:showyourworkyml}
-\end{itemize}
-
-\section{Automatic figure generation}
-\label{sec:auto-fig}
-%
-The workflow automatically determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file.
-Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
-Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
-%
-\begin{lstlisting}[
-    style=LaTeX,
-    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
-    emph={figures/eccentricity.pdf,fig:eccentricity},
-    emphstyle={\color{lsthilite}}
-]
-\begin{figure}
-  \begin{centering}
-    \includegraphics{figures/eccentricity.pdf}
-    \caption{...}
-    \label{fig:eccentricity}
-  \end{centering}
-\end{figure}
-\end{lstlisting}
-%
-The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
-Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which should be executed to produce that figure.
-By default, figure scripts are expected to be \texttt{Python} scripts, so in this case the workflow will attempt to run
-%
-\begin{lstlisting}[
-    style=bash
-]
-python eccentricity.py
-\end{lstlisting}
-%
-from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
-
-This behavior may be customized in several ways. 
-For instance, the figure script need not be a \texttt{Python} script; see \S\ref{sec:other-lang} for information on how to include scripts in any language.
-Another common scenario involves a script that generates multiple figures.
-These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script), or in multiple different figure environments by appending an arbitrary suffix to each figure label to make them all unique (i.e., \texttt{fig:eccentricity:one}, \texttt{fig:eccentricity:two}, etc.)
-And finally, this behavior may be overridden entirely by either placing the figure in the \texttt{src/static} directory (and committing it directly to the \texttt{GitHub} repository) or by supplying a label that instead begins with \texttt{fig*:}, which instructs the workflow to not attempt to programmatically generate the figure.
-In the latter case, a custom rule must be provided in the \texttt{Snakefile} to generate it (see, e.g., Figure~\ref{fig*:v1298tau}).
-
-\section{Support for other languages}
-\label{sec:other-lang}
-%
-Scripts in languages other than \texttt{Python} are supported via the inclusion of entries under the \texttt{scripts} key in the \texttt{showyourwork.yml} config file. 
-Consider Figure~\ref{fig:tree}, which was generated from the \texttt{TeX} file \texttt{figures/tree.tex}, which contains a \texttt{TikZ} picture. 
-In the main manuscript, we include the figure in the usual way, i.e.,
-%
-\begin{lstlisting}[
-    style=LaTeX,
-    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
-    emph={figures/eccentricity.pdf,fig:eccentricity},
-    emphstyle={\color{lsthilite}}
-]
-\begin{figure}
-  \begin{centering}
-    \includegraphics{figures/tree.pdf}
-    \caption{...}
-    \label{fig:tree}
-  \end{centering}
-\end{figure}
-\end{lstlisting}
-%
-By default, as we saw in \S\ref{sec:auto-fig}, this instructs the workflow to execute a file called \texttt{figures/tree.py} to generate the corresponding figure. 
-However, in the present case, that file does not exist; instead, we have a file called \texttt{figures/tree.tex}, which we would like to compile into a \texttt{PDF} using te \texttt{tectonic} engine.
-We can instruct the workflow to do this by specifying the following in \texttt{showyourwork.yml}:
-%
-\begin{lstlisting}[
-    style=yaml,
-    otherkeywords={script.path,script.name},
-    emph={script.path,script.name},
-    emphstyle={\color{lsthilite}}
-]
-scripts:
-  tex:
-    cd {script.path} && tectonic {script.name}
-\end{lstlisting}
-%
-Each entry under the \texttt{scripts} key should be a file extension, and under each one, a string containing a shell command that instructs the workflow how to execute a given {\color{lsthilite}\texttt{script}} to produce a given {\color{lsthilite}\texttt{output}}.
-For convenience, the following placeholders are recognized and expand as follows at runtime:
-%
-\begin{itemize}
-\item \texttt{\{script\}}: The full path to the input script.
-\item \texttt{\{script.path\}}: The full path to the directory containing the input script.
-\item \texttt{\{script.name\}}: The name of the input script (without the path).
-\item \texttt{\{output\}}: The full path to the output file.
-\item \texttt{\{output.path\}}: The full path to the directory containing the output file.
-\item \texttt{\{output.name\}}: The name of the output file (without the path).
-\end{itemize}
-%
-If additional customization is needed, such as the need to provide command-line arguments that are specific to individual figures, users should instead provide custom rules in the \texttt{Snakefile} (\S\ref{sec:arbitrary-rules}).
-
-\section{Arbitrary rules}
-\label{sec:arbitrary-rules}
-%
-Coming soon.
-
-\section{This paper}
-
-\begin{figure*}[p!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/dag.pdf}
-        \caption{
-            A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
-            Figure scripts are represented by black rectangles; helper scripts (such as ones imported by figure scripts or used in dataset generation) are similar, but have rounded edges.
-            Blue cylinders correspond to Zenodo records; blue boxes correspond to datasets.
-        }
-        \label{fig*:dag}
-    \end{centering}
-\end{figure*}
-
-\subsection{The \texttt{Snakefile}}
-\label{sec:Snakefile}
-%
-\lstinputlisting[
-    style=Snakefile
-]
-{../Snakefile}
-
-\subsection{The \texttt{showyourwork.yml} file}
-\label{sec:showyourworkyml}
-%
-\lstinputlisting[
-    style=yaml
-]
-{../showyourwork.yml}
-
-\subsection{The \texttt{environment.yml} file}
-\label{sec:environmentyml}
-%
-\lstinputlisting[
-    style=yaml
-]
-{../environment.yml}
 

### 2022-01-12 src/analysis/HD118203.py

@@ -1,118 +1,0 @@
-import exoplanet as xo
-import numpy as np
-import lightkurve as lk
-import pymc3 as pm
-import aesara_theano_fallback.tensor as tt
-import pymc3_ext as pmx
-from celerite2.theano import terms, GaussianProcess
-import warnings
-import logging
-
-# Suppress exoplanet & theano warnings
-logging.getLogger("theano.tensor.opt").setLevel(logging.ERROR)
-warnings.filterwarnings(action="ignore", category=UserWarning, module="exoplanet")
-
-# Download the light curve
-lcfs = lk.search_lightcurve(
-    "TIC 286923464", mission="TESS", author="SPOC"
-).download_all(flux_column="pdcsap_flux")
-lc = lcfs.stitch().remove_nans().remove_outliers(sigma=7)
-x = np.ascontiguousarray(lc.time.value, dtype=np.float64)
-y = np.ascontiguousarray(1e3 * (lc.flux - 1), dtype=np.float64)
-yerr = np.ascontiguousarray(1e3 * lc.flux_err, dtype=np.float64)
-texp = np.min(np.diff(x))
-
-# Run Box Least Squares (BLS) to obtain a guess for the planet period
-pg = xo.estimators.bls_estimator(x, y, yerr, min_period=2, max_period=20)
-peak = pg["peak_info"]
-period_guess = peak["period"]
-t0_guess = peak["transit_time"]
-depth_guess = peak["depth"]
-
-# Mask out-of-transit data
-transit_mask = (
-    np.abs((x - t0_guess + 0.5 * period_guess) % period_guess - 0.5 * period_guess)
-    < 0.25
-)
-x = np.ascontiguousarray(x[transit_mask])
-y = np.ascontiguousarray(y[transit_mask])
-yerr = np.ascontiguousarray(yerr[transit_mask])
-
-# Define our pymc3 model
-with pm.Model() as model:
-
-    # Stellar parameters
-    mean = pm.Normal("mean", mu=0.0, sigma=10.0)
-    u = xo.QuadLimbDark("u")
-    star_params = [mean, u]
-
-    # Gaussian process noise model
-    sigma = pm.InverseGamma("sigma", alpha=3.0, beta=2 * np.median(yerr))
-    log_sigma_gp = pm.Normal("log_sigma_gp", mu=0.0, sigma=10.0)
[…]

### 2022-01-12 src/figure-scripts/eccentricity.py

@@ -22,8 +22,11 @@ import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
-
+from pathlib import Path
 from astropy.visualization import quantity_support
+
+# Path to the `tex` directory
+TEX = Path(__file__).absolute().parents[1] / "tex"
 
 quantity_support()
 
@@ -148,4 +151,4 @@ ax.set_ylim(1e-20, 2e-18)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("eccentricity.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(TEX / "eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2022-01-12 src/figures/HD118203.py

@@ -1,54 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import corner
-
-# Load the results
-data = np.load("../data/HD118203.npz")
-x = data["x"]
-y = data["y"]
-gp_pred = data["gp_pred"]
-lc_pred = data["lc_pred"]
-map_t0 = data["map_t0"]
-map_period = data["map_period"]
-map_mean = data["map_mean"]
-samples = data["samples"]
-
-# Plot the transit
-fig = plt.figure(figsize=(8, 4))
-x_fold = (x - map_t0 + 0.5 * map_period) % map_period - 0.5 * map_period
-inds = np.argsort(x_fold)
-plt.scatter(x_fold, y - gp_pred - map_mean, c="k", s=3, alpha=0.5)
-plt.plot(x_fold[inds], lc_pred[inds] - map_mean, "C0")
-plt.xlabel("time since transit [days]", fontsize=16)
-plt.ylabel("relative flux [ppt]", fontsize=16)
-_ = plt.xlim(-0.25, 0.25)
-fig.savefig("HD118203_transit.pdf", bbox_inches="tight")
-
-# Plot the corner plot (with some appearance tweaks)
-samples[:, 0] -= 6.13498
-samples[:, 0] *= 1e5
-fig = corner.corner(
-    samples,
-    labels=[
-        "$P - P_0$ [days]",
-        "radius ratio",
-        "impact param",
-    ],
-    truths=[0, 0.05538, 0.125],
-)
-fig.axes[6].set_xticks([-4, -2, 0, 2, 4])
-fig.axes[6].set_xticklabels(
-    [
-        r"$-4 \times 10^{-5}$",
-        r"$-2 \times 10^{-5}$",
-        0,
-        r"$2 \times 10^{-5}$",
-        r"$4 \times 10^{-5}$",
-    ]
-)
-for axis in fig.axes:
-    for tick in axis.xaxis.get_major_ticks() + axis.yaxis.get_major_ticks():
-        tick.label.set_fontsize(6)
-    axis.set_xlabel(axis.get_xlabel(), fontsize=16)
-    axis.set_ylabel(axis.get_ylabel(), fontsize=16)
-fig.savefig("HD118203_corner.pdf", bbox_inches="tight")

### 2022-01-12 src/figures/helpers/sun.py

@@ -1,17 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-import numpy as np
-import astropy.constants as c
-
-
-__all__ = ["sun"]
-
-
-# Data for the Sun
-sun = {
-    "teff": 5772,
-    "prot": 25.4,
-    "e_prot": 25.4 - 24.5,
-    "E_prot": 36 - 25.4,
-    "logg": np.log10(c.GM_sun.cgs.value / c.R_sun.cgs.value ** 2),
-}

### 2022-01-12 src/figures/luhman16b.py

@@ -1,87 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import pickle
-
-
-# Load the dataset
-with open("../data/luhman16b.pickle", "rb") as f:
-    data = pickle.load(f, encoding="latin1")
-
-# Timestamps (from Ian Crossfield)
-t = np.array(
-    [
-        0.0,
-        0.384384,
-        0.76825872,
-        1.15339656,
-        1.5380364,
-        1.92291888,
-        2.30729232,
-        2.69268336,
-        3.07654752,
-        3.46219464,
-        3.8473428,
-        4.23171624,
-        4.61583456,
-        4.99971048,
-    ]
-)
-
-# Use the first epoch's wavelength array
-lams = data["chiplams"][0]
-
-# Interpolate onto that array
-observed = np.empty((14, 4, 1024))
-template = np.empty((14, 4, 1024))
-broadened = np.empty((14, 4, 1024))
-for k in range(14):
-    for c in range(4):
-        observed[k][c] = np.interp(
-            lams[c],
-            data["chiplams"][k][c],
-            data["obs1"][k][c] / data["chipcors"][k][c],
-        )
-        template[k][c] = np.interp(
-            lams[c],
-            data["chiplams"][k][c],
-            data["chipmodnobroad"][k][c] / data["chipcors"][k][c],
-        )
-        broadened[k][c] = np.interp(
-            lams[c],
-            data["chiplams"][k][c],
-            data["chipmods"][k][c] / data["chipcors"][k][c],
-        )
-
-# Get the final data arrays
-wav = data["chiplams"][:, 2]
-flux = data["obs1"][:, 2] / data["chipcors"][:, 2]
-model = data["chipmods"][:, 2] / data["chipcors"][:, 2]
-
-# Plot the spectra
-fig, ax = plt.subplots(1, figsize=(8, 5))
-fig.subplots_adjust(wspace=0.1)
-for k in range(14):
-    ax.plot(wav[k], 0.65 * k + flux[k], "k.", ms=2, alpha=0.5, zorder=-1)
-    ax.plot(wav[k], 0.65 * k + model[k], "C1-", lw=1)
-
-# Appearance hacks
-ax.spines["left"].set_visible(False)
[…]

### 2022-01-12 src/figures/rossbyridge.py

@@ -1,43 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-from helpers.sun import sun
-
-# McQuillan et al. 2014
-mcq = pd.read_csv("../data/McQuillan2014.csv")
-mcq = mcq.add_prefix("mcq_")
-
-# LAMOST-Kepler
-lam = pd.read_csv("../data/KeplerRot-LAMOST.csv")
-
-# Drop duplicate sources, keeping the one with the brighter G magnitude
-lam = lam.sort_values(["KIC", "Gmag"], ascending=(True, True))
-lam = lam.merge(mcq, how="left", left_on="KIC", right_on="mcq_KIC")
-lam = lam.drop_duplicates(subset=["KIC"], keep="first")
-lam_mask = lam["Teff_lam"] > 3000
-lam_mask = lam["Teff_lam"] < 8000
-lam_mask &= lam["logg_lam"] > 3
-lam_mask &= lam["logg_lam"] < 5
-lam_mask &= abs(lam["feh_lam"]) < 2
-lam = lam[lam_mask]
-
-# Plot
-fig, ax = plt.subplots(1, figsize=(4, 4))
-ax.scatter(lam["Teff_lam"], lam["mcq_Prot"], marker=".", rasterized=True, s=0.1)
-ax.set_xlabel("Effective temperature [K]")
-ax.set_xlim(7250, 3250)
-ax.set_ylim(-2, 60)
-ax.plot(sun["teff"], sun["prot"], "o", color="C1")
-ax.errorbar(
-    sun["teff"],
-    sun["prot"],
-    yerr=np.vstack([sun["e_prot"], sun["E_prot"]]),
-    fmt="o",
-    color="C1",
-    mec="white",
-    ms=6,
-)
-ax.set_ylabel("Rotation period [d]")
-fig.savefig("rossbyridge.pdf", bbox_inches="tight", dpi=100)

### 2022-01-13 src/figure-scripts/eccentricity.py
woot

@@ -25,8 +25,8 @@ import matplotlib.pyplot as plt
 from pathlib import Path
 from astropy.visualization import quantity_support
 
-# Path to the `tex` directory
-TEX = Path(__file__).absolute().parents[1] / "tex"
+# Path to the `tex/figures` directory
+FIGURES = Path(__file__).absolute().parents[1] / "tex" / "figures"
 
 quantity_support()
 
@@ -151,4 +151,4 @@ ax.set_ylim(1e-20, 2e-18)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig(TEX / "eccentricity.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(FIGURES / "eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2022-01-14 src/tex/ms.tex
restructure
beauty

@@
 \documentclass[twocolumn]{aastex631}
+\usepackage{showyourwork}
 
@@
 % Title
-\title{\showyourwork: a workflow for open source scientific articles}
+\title{A workflow for open source scientific articles}
 
@@
         \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
-        \caption{
-            The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2021}. 
-            This figure was automatically generated from the script \texttt{src/figures/eccentricity.py}.
-        }
+        \caption{Foo}
         \label{fig:eccentricity}
@@
         \includegraphics[width=\linewidth]{figures/banner.png}
-        \caption{
-            The default \texttt{README.md} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
-            Note that since this figure is a screenshot, we place it in the \texttt{src/static} folder and \texttt{git}-commit it.
-            The workflow skips the generation step for any figures in that directory; note the absence of a margin icon next to this caption.
-        }
+        \caption{FOO}
         \label{fig:banner}

### 2022-01-16 src/data/paths.py
paths

@@ -1,0 +1,1 @@
+../../showyourwork/workflow/utils/paths.py

### 2022-01-16 src/figure-scripts/eccentricity.py

@@ -17,16 +17,12 @@ frequency at which the ma- jority of the gravitational wave signal
 is concentrated.
 
 """
-
+import paths
 import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
-from pathlib import Path
 from astropy.visualization import quantity_support
-
-# Path to the `tex/figures` directory
-FIGURES = Path(__file__).absolute().parents[1] / "tex" / "figures"
 
 quantity_support()
 
@@ -151,4 +147,4 @@ ax.set_ylim(1e-20, 2e-18)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig(FIGURES / "eccentricity.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(paths.figures / "eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2022-02-09 src/figure-scripts/eccentricity.py
misc

@@ -1,150 +1,0 @@
-"""
-This is the script that generates Figure 3 in Wagg et al. (2021).
-
-Original version:
-
-https://github.com/TeamLEGWORK/LEGWORK-paper/blob/d0afa5/src/figures/role_eccentricity.py
-
-Original caption:
-
-An illustration of the effect of eccentricity on the detectability 
-of a LISA source. The three sets of points are coloured by their 
-eccentricity and each individual point corresponds to a harmonic 
-frequency, where its height above the curve gives its SNR. We 
-annotate each set of points with its total SNR and overlay the 
-LISA sensitivity curve. The dotted vertical lines indicate the 
-frequency at which the ma- jority of the gravitational wave signal 
-is concentrated.
-
-"""
-import paths
-import legwork as lw
-import numpy as np
-import astropy.units as u
-import matplotlib.pyplot as plt
-from astropy.visualization import quantity_support
-
-quantity_support()
-
-plt.rc("font", family="serif")
-plt.rcParams["text.usetex"] = False
-fs = 24
-
-# update various fontsizes to match
-params = {
-    "figure.figsize": (12, 8),
-    "legend.fontsize": fs,
-    "axes.labelsize": fs,
-    "xtick.labelsize": 0.9 * fs,
-    "ytick.labelsize": 0.9 * fs,
-    "axes.linewidth": 1.1,
-    "xtick.major.size": 7,
-    "xtick.minor.size": 4,
-    "ytick.major.size": 7,
-    "ytick.minor.size": 4,
-}
-plt.rcParams.update(params)
-
-# set eccentricities
-ecc = np.array([1e-6, 0.6, 0.9])
-n_binaries = len(ecc)
-
-# use constant values for mass, f_orb and distance
-m_1 = np.repeat(0.6, n_binaries) * u.Msun
-m_2 = np.repeat(0.6, n_binaries) * u.Msun
-f_orb = np.repeat(1.5e-3, n_binaries) * u.Hz
-dist = np.repeat(15, n_binaries) * u.kpc
-
-# get the SNR in each harmonic
-snr2_n = lw.snr.snr_ecc_evolving(
-    m_1=m_1,
-    m_2=m_2,
-    f_orb_i=f_orb,
-    ecc=ecc,
-    dist=dist,
-    harmonics_required=100,
-    t_obs=4 * u.yr,
[…]

### 2022-02-09 src/figure-scripts/random_numbers.py

@@ -1,0 +1,10 @@
+import paths
+import matplotlib.pyplot as plt
+import numpy as np
+
+data = np.loadtxt(paths.data / "random_numbers.dat")
+
+fig = plt.figure()
+plt.plot(data)
+
+fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-09 src/figure-scripts/zenodo_example.py

@@ -1,0 +1,18 @@
+import paths
+import matplotlib.pyplot as plt
+
+datasets = [
+    "A.dat",
+    "baz/B.dat",
+    "foo/C.dat",
+    "foo/bar/H.dat",
+    "G.dat",
+    "C.dat",
+    "bar/H.dat",
+    "G_copy.dat",
+]
+
+for dataset in datasets:
+    assert (paths.data / dataset).exists()
+
+plt.figure().savefig(paths.figures / "zenodo_example.pdf", bbox_inches="tight")

### 2022-02-09 src/scripts/generate_random_numbers.py

@@ -1,0 +1,10 @@
+import paths
+import numpy as np
+
+# Get the seed from the rule parameters
+seed = snakemake.params["seed"]
+
+# Write 10 random numbers to the dataset
+np.random.seed(seed)
+X = np.random.randn(10)
+np.savetxt(str(paths.data / "random_numbers.dat"), X)

### 2022-02-09 src/figure-scripts/random_numbers.py
better idea

@@ -6,5 +6,4 @@ data = np.loadtxt(paths.data / "random_numbers.dat")
 
 fig = plt.figure()
 plt.plot(data)
-
 fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/figure-scripts/many_datasets.py
woot zenodo

@@ -1,0 +1,12 @@
+import paths
+import matplotlib.pyplot as plt
+import numpy as np
+
+datasets = (paths.data / "many_datasets").glob("*.dat")
+fig = plt.figure()
+
+for dataset in datasets:
+    data = np.loadtxt(dataset)
+    plt.plot(data)
+
+fig.savefig(paths.figures / "many_datasets.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/scripts/generate_many_datasets.py

@@ -1,0 +1,14 @@
+import paths
+import numpy as np
+
+# Get the seed from the rule parameters
+seed = snakemake.params["seed"]
+
+# Write 10 random numbers to 5 different datasets
+if not (paths.data / "many_datasets").exists():
+    (paths.data / "many_datasets").mkdir()
+
+np.random.seed(seed)
+for n in range(1, 6):
+    X = np.random.randn(10)
+    np.savetxt(str(paths.data / "many_datasets" / f"{n:02d}.dat"), X)

### 2022-02-15 src/figure-scripts/random_numbers.py
dummy commit

@@ -4,6 +4,7 @@ import numpy as np
 
 data = np.loadtxt(paths.data / "random_numbers.dat")
 
+#
 fig = plt.figure()
 plt.plot(data)
 fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/figure-scripts/random_numbers.py
dummy commit

@@ -4,7 +4,6 @@ import numpy as np
 
 data = np.loadtxt(paths.data / "random_numbers.dat")
 
-#
 fig = plt.figure()
 plt.plot(data)
 fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/figure-scripts/random_numbers.py
debug

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 data = np.loadtxt(paths.data / "random_numbers.dat")
-
+#
 fig = plt.figure()
 plt.plot(data)
 fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/figure-scripts/random_numbers.py
debug

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 data = np.loadtxt(paths.data / "random_numbers.dat")
-#
+
 fig = plt.figure()
 plt.plot(data)
 fig.savefig(paths.figures / "random_numbers.pdf", format="pdf", bbox_inches="tight")

### 2022-02-15 src/figure-scripts/random_numbers.py
debug

@@ -2,7 +2,6 @@ import paths
 import matplotlib.pyplot as plt
 import numpy as np
 
-
 data = np.loadtxt(paths.data / "random_numbers.dat")
 
 fig = plt.figure()

### 2022-02-15 src/figure-scripts/random_numbers.py
dummy commit

@@ -2,6 +2,7 @@ import paths
 import matplotlib.pyplot as plt
 import numpy as np
 
+
 data = np.loadtxt(paths.data / "random_numbers.dat")
 
 fig = plt.figure()
